---
title: "Using daedalus.data and daedalus"
output: rmarkdown::html_vignette
bibliography: resources/references.json
link-citations: true
vignette: >
  %\VignetteIndexEntry{Using daedalus.data and daedalus}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

_daedalus.data_ is a package to handle input data files to use in the DAEDALUS model. The idea behind the development of this package is to have the flexibility to 
* Update or otherwise modify the input data without needing to update the model package itself 
* Curate reference websites for the source data files and develop semi-automated workflows to maintain them up-to-date
* Ensure compatibility of the input data with the working version of the _daedalus_ model

This vignette demonstates how to use _daedalus.data_ with the DAEDALUS model, as adapted from @haw2022 in R. The package provides data from @walker2020 on country demography, country workforce per economic sector, and social contacts between age groups in `country_data`.
The package also provides data from @jarvis2024 on workplace contacts in economic sectors.
Both datasets are accessed by internal functions to reduce the need for user input.

```{r libraries}
library(daedalus.data)
library(daedalus)
```

## References
